Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-30 paper/gd1.tex
Captions

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{gd1_sample.pdf}
\end{center}
\caption{
On-sky positions of likely GD-1 members, in the coordinate system aligned with the stream.
GD-1 is apparent as an overdensity in retrograde proper motions (orange box on the top right panel), so a proper motion selection already reveals the stream in positions of individual stars (top left).
The stream population is older and more metal poor than the field Milky Way population, so the stream also stands out in the color-magnitude diagram (bottom right).
Additional photometric selection of the stream's main sequence (orange region in the CMD) unveils the stream in unprecedented detail (bottom left).
This map extends the stream by $20^\circ$, identifies a plausible location of the progenitor at $\phi_1\sim13^\circ$, confirms the existence of a significant gap at $\phi_1\sim-20^\circ$, shows additional under-densities at $\phi_1\sim-40^\circ,-5^\circ$ and for the first time finds stream overdensities off from the main track of a cold stream at $(\phi_1,\phi_2)\sim(-35^\circ,-1^\circ)$ and $(-15^\circ,-2^\circ)$.
}
\label{fig:selection}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars selected using \gaia\
proper motions and \pans\ photometry.
Lines show a 2nd-order polynomial fit to the median stream track offset by $\pm
0.75^\circ$; the region between these lines is adopted as the nomial stream
region.
\textit{Panel (b)}: Sky positions of simulated star particles from a toy mock
stream model of the GD-1 stream track.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
running, overlapping $3^\circ$ windows for both GD-1 data and toy model.
\textit{Panel (d)}: Median proper motion along the stream longitude computed in
the same bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{orbitfit.pdf}
\end{center}
\caption{%
Best-fitting orbit in a simple (fixed) model for the gravitational potential of
the Milky Way using phase-space information along the stream measured from this
work combined with data from \citet{Koposov:2010}.
Left panel shows the orbit in Galactocentric cylindrical radius, $R$, and height
above the Galactic midplane, $z$;
grey line at $z=0$ shows the approximate radius of the disk.
Right panel shows the orbit projected onto the midplane in Galactocentric
cartesian coordinates.
The darker orbit section highlights the range of stream longitudes over which we
clearly see GD-1 stream stars in \figurename~\ref{fig:selection}.
Note that GD-1 is retrograde with respect to the disk (see approximate location
and direction of motion of the sun in right panel, $\odot$).
}
\label{fig:orbitfit}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{gd1_sample.pdf}
\end{center}
\caption{
On-sky positions of likely GD-1 members in the GD-1 coordinate system.
GD-1 is apparent as an overdensity in negative proper motions (top right panel,
orange box), so selecting on proper motion already reveals the stream in
positions of individual stars (top left).
The stream also stands out in the color-magnitude diagram (bottom right) as
older and more metal poor than the background.
Selecting the main sequence of GD-1 (orange, shaded region in bottom right)
along with proper motion cuts unveils the stream in unprecedented detail (bottom
left).
% This map extends the stream by $20^\circ$, identifies a plausible location of the progenitor at $\phi_1\sim13^\circ$, confirms the existence of a significant gap at $\phi_1\sim-20^\circ$, shows additional under-densities at $\phi_1\sim-40^\circ,-5^\circ$ and for the first time finds stream overdensities off from the main track of a cold stream at $(\phi_1,\phi_2)\sim(-35^\circ,-1^\circ)$ and $(-15^\circ,-2^\circ)$.
}
\label{fig:selection}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars.
Lines show a 2nd-order polynomial fit to the median stream track offset by $\pm
0.75^\circ$; the enclosed region is adopted as the nominal stream region.
\textit{Panel (b)}: Sky positions of simulated star particles from a mock stream
model of the GD-1 stream.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
successive, overlapping $3^\circ$ windows for both GD-1 data and the model
stream.
\textit{Panel (d)}: Median proper motion along the stream computed in the same
bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{orbitfit.pdf}
\end{center}
\caption{%
Best-fit orbit in a simple model for the gravitational potential of the Milky
Way using \gaia\ proper motions and the filtered stream track.
Left panel shows the orbit in Galactocentric cylindrical radius, $R$, and
position above the Galactic midplane, $z$;
gray line at $z=0$ shows the approximate radius of the disk.
Right panel shows the orbit projected onto the midplane in Galactocentric
cartesian coordinates, ($x$, $y$).
Darker orbit section highlights the stream longitudes over which we clearly see
GD-1 stream stars.
Note that GD-1 is retrograde with respect to the disk (location and direction of
motion of the sun are indicated in the right panel, $\odot$).
}
\label{fig:orbitfit}
\end{figure}
